
# Read in packages
```
require(ggplot2)
require(plyr)
require(lubridate)
require(dplyr)
require(sp)
require(maptools)
require(ggmap)
require(ggplot2)
require(reshape2)
require(rgdal)
require(raster)
require(rgeos)
require(PBSmapping)
require(gdistance)
require(ggrepel)
```

# Practicing with Morris et al paper data
```{r}
setwd("C:/Users/keyserf/Documents/")

### read in data on farmed escapes from Morris et al paper

morris <- read.csv("./Data/Morris et al 2008 data.csv")
str(morris)

# ### convert formatting and get rid of "bad" rows
# 
# morris$Year <- as.character(morris$Year)
# morris$YearSimp <- as.numeric(morris$Year)
# 
# morris$PropFarmed <- as.character(morris$PropFarmed)
# morris$PropSimp <- as.numeric(morris$PropFarmed)
# 
# morris$clean <- ifelse(is.na(morris$YearSimp) == "TRUE" | is.na(morris$PropSimp)=="TRUE", "BAD", "GOOD")
# 
# morris_clean <- subset(morris, clean=="GOOD")
# 
# ### subset by province
# morris_cleanME <- subset(morris_clean, ProvState=="ME")
# morris_cleanNB <- subset(morris_clean, ProvState=="NB")
# morris_cleanNL <- subset(morris_clean, ProvState=="NL")
# morris_cleanNS <- subset(morris_clean, ProvState=="NS")
# 
# ### plot by province
# plot1 <- ggplot() + geom_point(data=morris_cleanME, aes(YearSimp, PropSimp)) + theme_bw() +
#   facet_grid(~River)
# plot2 <- ggplot() + geom_point(data=morris_cleanNB, aes(YearSimp, PropSimp)) + theme_bw() +
#   facet_grid(~River)
# plot3 <- ggplot() + geom_point(data=morris_cleanNL, aes(YearSimp, PropSimp)) + theme_bw() +
#   facet_grid(~River)
# plot4 <- ggplot() + geom_point(data=morris_cleanNS, aes(YearSimp, PropSimp)) + theme_bw() +
#   facet_grid(~River)

# require(gridExtra)
# 
# grid.arrange(plot1, plot2, plot3, plot4, nrow=4)
# 
# write.csv(morris_clean, "./Data/morris_clean.csv")
# 
# morris_clean <- read.csv("C:/Users/keyserf/Documents/Data/morris_clean.csv", header=TRUE)

### plot NS escapes
## http://ftp.geogratis.gc.ca/pub/nrcan_rncan/vector/canvec/shp/Land/
# NS.low <- readOGR(dsn = "C:/Users/keyserf/Documents/R/canvec/canvec_250K_NS_Hydro_shp/waterbody_2.shp", layer="waterbody_2")
NS.low <- crop(NS.low, extent(-66.25, -59.5, 43.4, 47.5))
NSprov <- fortify(NS.low)
rm(NS.low)

## http://ftp.geogratis.gc.ca/pub/nrcan_rncan/vector/canvec/shp/Land/
# NB.low <- readOGR(dsn = "C:/Users/keyserf/Documents/R/canvec/canvec_250K_NB_Hydro_shp/waterbody_2.shp", layer="waterbody_2")
NBprov <- fortify(NB.low)
rm(NB.low)

## http://ftp.geogratis.gc.ca/pub/nrcan_rncan/vector/canvec/shp/Land/
# PE.low <- readOGR(dsn = "C:/Users/keyserf/Documents/R/canvec/canvec_250K_PE_Hydro_shp/waterbody_2.shp", layer="waterbody_2")
PEprov <- fortify(PE.low)
rm(PE.low)

## http://www.maine.gov/megis/catalog/
# ME.low <- readOGR(dsn = "C:/Users/keyserf/Documents/R/canvec/bathym100s/bathym100.shp", layer="bathym100")
# MEst <- fortify(ME.low)
# summary(MEst$long)
# MEst$long <- -MEst$long/10000
# MEst$lat <- MEst$lat/100000

nsrivers <- as.data.frame(unique(morris_clean$River[morris_clean$Prov=="NS"]))
names(nsrivers) <- c("river")
coords_clean <- rbind(c(44.778122, -65.439294), 
               c(46.094226, -60.857244),
               c(45.109829, -64.275097),
               c(45.610836, -60.626756),
               c(44.310002, -64.390153),
               c(44.047893, -64.709702),
               c(46.082903, -60.909614),
               c(44.939173, -65.055891),
               c(46.299002, -60.615435),
               c(44.052819, -66.169571),
               c(45.298904, -63.479638),
               c(45.953641, -61.102664))
nsrivers <- cbind(nsrivers, coords_clean)

nsrivers_other <- unique(subset(morris, ProvState=="NS", select="River"))
names(nsrivers_other) <- "river"
nsrivers_other <- anti_join(nsrivers_other, nsrivers)
nsrivers_other
coords_rough <- rbind(c(43.842299, -65.991485),
                      c(44.729245, -63.662550),
                      c(46.218702, -60.610511),
                      c(45.050054, -61.892250),
                      c(45.865024, -60.802479),
                      c(45.409762, -64.098723),
                      c(46.368190, -60.525074),
                      c(44.611538, -65.676093),
                      c(46.428359, -61.095991),
                      c(45.003232, -62.087995),
                      c(44.220810, -66.143551),
                      c(45.399889, -64.326540),
                      c(45.966662, -61.115833))
nsrivers_other <- cbind(nsrivers_other, coords_rough)
                      
nsrivers_all <- rbind(nsrivers, nsrivers_other)
names(nsrivers_all) <- c("River", "lat", "long")

nsmorris <- subset(morris, ProvState=="NS")
nsmorris <- join(nsmorris, nsrivers_all, type="left")

unique(nsmorris$TotalFarmed)

nsmorris_true <- subset(nsmorris, !TotalFarmed =="0", select=c("River", "lat", "long", "TotalFarmed"))
nsmorris_true <- subset(nsmorris_true, !TotalFarmed =="N/A")
nsmorris_true <- unique(nsmorris_true[,1:3])

## NB
nbrivers <- as.data.frame(unique(morris$River[morris$ProvState=="NB"]))
names(nbrivers) <- c("river")
coords_clean <- rbind(c(45.545066, -66.011293), 
               c(45.422197, -65.402976),
               c(45.262844, -65.781699),
               c(45.179130, -66.987045),
               c(45.131204, -67.068731),
               c(45.199799, -67.261215),
               c(45.118038, -66.876022),
               c(47.074048, -65.399438),
               c(45.570888, -65.774480),
               c(45.957255, -66.618207),
               c(45.502517, -66.072903),
               c(45.167935, -67.194878),
               c(45.610963, -64.957627),
               c(45.206954, -67.147044))
nbrivers <- cbind(nbrivers, coords_clean)

names(nbrivers) <- c("River", "lat", "long")

nbmorris <- subset(morris, ProvState=="NB")
nbmorris <- join(nbmorris, nbrivers, type="left")

unique(nbmorris$TotalFarmed)

nbmorris_true <- subset(nbmorris, !TotalFarmed =="0", select=c("River", "lat", "long", "TotalFarmed"))
nbmorris_true <- subset(nbmorris_true, !TotalFarmed =="N/A")
nbmorris_true <- unique(nbmorris_true[,1:3])

CAshp <- readOGR(dsn = "C:/Users/keyserf/Documents/R/canvec/canvec_1M_CA_Land_shp/shoreline_1.shp", layer="shoreline_1")
# CA.low <- crop(CAshp, extent(-67.7, -59.5, 43.2, 48.1))
# CA.map <- fortify(CA.low, region="id")
# rm(NS.low)
# 
# CA.low@data$id <- rownames(CA.low@data)
# CA.low.points <- fortify(CA.low, region="id")
# CA.df = join(CA.low.points, CA.low@data, by="id")

## http://www.gulfofmaine-census.org/data-mapping/gis-data-layers/
## http://pubs.usgs.gov/of/2003/of03-001/data/basemaps/
GOM <- readOGR(dsn = "C:/Users/keyserf/Documents/R/canvec/PhysioRegions_WGS84.shp", layer="PhysioRegions_WGS84")
GOMclip <- gDifference(GOM, NB.low)
GOMclip <- fortify(GOMclip)

## using shapefiles from AQ Sites NB_2016-11-22.R
NSmorrismap <- ggplot() + 
  #ggtitle("Maritimes salmon rivers")+
  #geom_polygon(data=NBprov, aes(long, lat, group=group), fill="grey") +
  geom_spatial(data=NB.low, aes(fill=ctry_en)) +
  #geom_polygon(data=PEprov, aes(long, lat, group=group), fill="grey") +
  geom_spatial(data=PE.low, aes(fill=ctry_en)) +
  #geom_polygon(data=NSprov, aes(long, lat, group=group), fill="grey") +
  geom_spatial(data=NS.low, aes(fill=ctry_en)) +
  scale_fill_manual(values=c("grey"), guide=FALSE) +
  geom_polygon(data=GOMclip, aes(long, lat, group=group), fill="grey") +
  geom_path(data=CA.df, aes(long, lat, group=group),colour="black") +
  annotate(geom="rect", xmin=-60, xmax=-59.5, ymin=47.5, ymax= 48, fill="grey") +
  annotate(geom="rect", xmin=-64, xmax=-59.5, ymin=43.2, ymax= 44, fill="grey") +
  annotate(geom="rect", xmin=-61, xmax=-59.5, ymin=44, ymax= 45, fill="grey") +
  geom_point(data=nsrivers_all, aes(long, lat), shape=21, fill="blue", colour="black", size=5) +
  geom_point(data=nsmorris_true, aes(long, lat), size=5, fill="red", shape=21, colour="black") +
  #geom_label_repel(data=nsrivers_all, aes(long, lat, label=River), size=3, point.padding = unit(0.5,"lines"), min.segment.length = unit(0.1, "lines"))+
  geom_point(data=nbrivers, aes(long, lat), shape=21, fill="blue", colour="black", size=5) +
  geom_point(data=nbmorris_true, aes(long, lat), size=5, fill="red", shape=21, colour="black") +
  #geom_label_repel(data=nbrivers, aes(long, lat, label=River), size=3, point.padding = unit(0.5,"lines"), min.segment.length = unit(0.1, "lines"))+
  coord_map(xlim=c(-67.7, -59.5), ylim=c(43.2, 48)) +
  theme_classic() +
  theme(panel.background = element_blank(), panel.border=element_rect(colour="black", fill=NA)) 


## NL
nlrivers <- as.data.frame(unique(morris$River[morris$ProvState=="NL"]))
names(nlrivers) <- c("river")
coords_clean <- rbind(c(47.870898, -55.751851), 
               c(47.75613, -55.84686))
nlrivers <- cbind(nlrivers, coords_clean)

names(nlrivers) <- c("River", "lat", "long")

nlmorris <- subset(morris, ProvState=="NL")
nlmorris <- join(nlmorris, nlrivers, type="left")

unique(nlmorris$TotalFarmed)

nlmorris_true <- subset(nlmorris, !TotalFarmed =="0", select=c("River", "lat", "long", "TotalFarmed"))
nlmorris_true <- subset(nlmorris_true, !TotalFarmed =="N/A")
nlmorris_true <- unique(nlmorris_true[,1:3])

CA.NL <- crop(CAshp, extent(-60, -52, 46.5, 52))
CA.NL@data$id <- rownames(CA.NL@data)
CA.NL.points <- fortify(CA.NL, region="id")
CA.NL.df = join(CA.NL.points, CA.NL@data, by="id")

NL.low <- crop(NL.low, extent(-59.92, -52.3, 46.52, 51.78))

NLmorrismap <- ggplot() + 
  #ggtitle("Maritimes salmon rivers")+
  #geom_polygon(data=NBprov, aes(long, lat, group=group), fill="grey") +
  geom_spatial(data=NL.low, aes(fill=ctry_en)) +
  scale_fill_manual(values=c("grey"), guide=FALSE) +
  geom_path(data=CA.NL.df, aes(long, lat, group=group),colour="black") +
  annotate(geom="rect", xmin=-60, xmax=-56.5, ymin=46.5, ymax= 47.25, fill="grey") +
  annotate(geom="rect", xmin=-60, xmax=-56.1, ymin=46.5, ymax= 47.4, fill="grey") +
  annotate(geom="rect", xmin=-60, xmax=-59.42, ymin=46.5, ymax= 50.21, fill="grey")+
  annotate(geom="rect", xmin=-56.1, xmax=-55.9, ymin=46.5, ymax= 46.83, fill="grey") +
  annotate(geom="rect", xmin=-54, xmax=-52.2, ymin=50, ymax= 51.8, fill="grey") +
  geom_point(data=nlrivers, aes(long, lat), shape=21, fill="blue", colour="black", size=5) +
  geom_point(data=nlmorris_true, aes(long, lat), size=5, fill="red", shape=21, colour="black") +
  #geom_label_repel(data=nbrivers, aes(long, lat, label=River), size=3, point.padding = unit(0.5,"lines"), min.segment.length = unit(0.1, "lines"))+
  coord_map(xlim=c(-59.9, -52.3), ylim=c(46.52, 51.79)) +
  theme_classic() +
  theme(panel.background = element_blank(), panel.border=element_rect(colour="black", fill=NA)) 

NLmorrismap + annotate(geom="rect", xmin=-60, xmax=-59.42, ymin=46.5, ymax= 50.21, fill="pink")

require(gridExtra)
grid.arrange(NSmorrismap, NLmorrismap, ncol=2)


```


##########################################################################################################################
######################### SOUTHERN NEWFOUNDLAND CAGE SITE DISTANCES TEMPLATE CODE ########################################
##########################################################################################################################

## read in NL open cage site coordinates
```{r}
sites <- read.csv("C:/Users/keyserf/Documents/Data/NL Stocking 2010-2013.csv")
str(sites)
```

## for low-res generic mapping
```{r}
## http://ftp.geogratis.gc.ca/pub/nrcan_rncan/vector/atlas/75m_prod/geog/shape/
prov <- readShapeSpatial("./R/canvec/pvp/pvp.shp", proj4string=CRS("+proj=longlat +ellps=GRS80 +no_defs"))
#prov <- fortify(model=prov)
```

## General plots
```{r}
## Number of fish per site
ggplot() + 
  geom_polygon(data=prov, aes(long, lat, group=group), fill="grey")+
  geom_point(data=sites, aes(Long, Lat, size=Fish.Remaining...site), colour="red", shape=21) + 
  facet_wrap(~Year, nrow=4) +
  theme_bw() +
  coord_fixed(ratio=1.5, xlim=c(-57, -55), ylim=c(47, 48)) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank()) +
  scale_size_continuous(name="Number\nof fish")

## Number of cages per site
ggplot() + 
  geom_polygon(data=prov, aes(long, lat, group=group), fill="grey")+
  geom_point(data=sites, aes(Long, Lat, size=Number.of.Cages), colour="red", shape=21) + 
  facet_wrap(~Year, nrow=4) +
  theme_bw() +
  coord_fixed(ratio=1.5, xlim=c(-57, -55), ylim=c(47, 48)) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank()) +
  scale_size_continuous(name="Number\nof cages")
```


## Calculate distances between points with boundaries, need fine scale data for raster
## SKIP DOWN IF ENVIRONMENT IS LOADED
### read in shapefiles, create raster file
```{r}
## http://ftp.geogratis.gc.ca/pub/nrcan_rncan/vector/canvec/shp/Hydro/
#NL <- readOGR(dsn = "./R/canvec/canvec_50K_NL_Hydro_shp/waterbody_2_1.shp", layer="waterbody_2_1")
## THIS TAKES WAY TOO LONG, try lower resolution:
## http://ftp.geogratis.gc.ca/pub/nrcan_rncan/vector/canvec/shp/Land/
## NL.low <- readOGR(dsn = "C:/Users/keyserf/Documents/R/canvec/canvec_250K_NL_Hydro_shp/waterbody_2.shp", layer="waterbody_2")

# #cropping shapefile to the area and details I need
# NL.low.ocean <- crop(NL.low, extent(-57, -54, 47, 48))
# NL.low.ocean <- subset(NL.low.ocean, perm_en=="Permanent")
# writeOGR(obj=NL.low.ocean, dsn="canvec", layer="NL.low.ocean", driver="ESRI Shapefile")
# rm(NL.low)

# read in cropped shapefile: NL.low.ocean
# NL.low.ocean <- readOGR(dsn="C:/Users/keyserf/Documents/R/canvec/NL.low.ocean.dbf", layer="NL.low.ocean")
# plot(NL.low.ocean)
# points(siterast, pch=16, col="red")

# # creating raster
# r <- raster(ncol=1125, nrow=560)
# extent(r) <- extent(NL.low.ocean)
# NLrast <- rasterize(NL.low.ocean, r, fun="first")

```

##### START HERE IF ENVIRONMENT IS READY #####
```{r}
# site coords
x <- sites$Long
y <- sites$Lat
xy <- cbind(x, y)
siterast <- as.matrix(xy)

# escaped fish location
escapes <- read.csv("C:/Users/keyserf/Documents/Data/Gillnetting2015 - Master Copy.csv")
str(escapes)

escapes <- subset(escapes, Life.Stage == "Farmed")

escapelocs <- unique(select(escapes, Latitude..N., Longitude..E.))
escapemat <- as.matrix(cbind(escapelocs$Longitude..E., escapelocs$Latitude..N.))

```

## River mouths
```{r}
## To get river mouth locations, use click(). Click on the plot to get coords for the river mouths with sampling sites on them.
plot(NLrast)
text(escapelocs$Longitude..E., escapelocs$Latitude..N.)
lines(NLline)
# rivermouths <- SpatialPoints(click(n=3))
rivermouths <- snapPointsToLines(rivermouths, NLline)
rivermouths <- fortify(as.data.frame(rivermouths))
text(rivermouths$X, rivermouths$Y, col="yellow")

```

# SKIP IF ENVIRONMENT LOADED! change values in raster so that land is impassable (i.e. distances would be massive). 
```{r}
# Also get rid of ocean blob
# NLrast@data@values <- ifelse(is.na(NLrast@data@values)=="TRUE", 10000, 1)
# NLrast@data@values <- ifelse(coordinates(NLrast)[,1] < -56 & coordinates(NLrast)[,2] < 47.4, 1, NLrast@data@values)
```

# Transition layer, Geocorrection, calculate distance matrix, find shortest distance
```{r}
# create transition layer for raster (likelihood of presence within cell). 
tr3 <- transition(1/NLrast, transitionFunction=mean, directions=8)
tr3c <- geoCorrection(tr3, type="c")
plot(NLrast)

# calculate least-cost distance between siterast (site location) and testrast (escaped fish location)
d3 <- costDistance(tr3c, fromCoords = siterast, toCoords = cbind(rivermouths$X, rivermouths$Y))
d3 

# calculate cumulative weighted distance. for each river: sum(1/distance to each AQ site)
cum.wt.dist <- apply(d3, 2, function(x) sum(1/x))

riverCWD <- data.frame(lat=rivermouths[,3], long = rivermouths[,2], cum.wt.dist = cum.wt.dist)

```

### match rivermouths to sampling sites
```{r}
escapelocs$rivermouth <- c(2,2,2,2,1,3)

riverCWD$rivermouth <- c(1,2,3)

escapelocs <- join(escapelocs, riverCWD, type="left")

escapelocs$FYCWD <- sum(inventory$totalfish)/escapelocs$cum.wt.dist


plot1 <- ggplot() + 
  geom_polygon(data=prov, aes(long, lat, group=group), fill="grey")+
  geom_point(data=inventory, aes(Long, Lat, size=totalfish), fill="red", shape=21, colour="black") + 
  theme_bw() +
  coord_map(xlim=c(-56.4, -55.0), ylim=c(47.4, 47.8)) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank()) +
  scale_size_continuous(name="totalfish")

plot2 <- ggplot() + 
  geom_polygon(data=prov, aes(long, lat, group=group), fill="grey")+
  geom_point(data=escapelocs, aes(long, lat, size=FYCWD), fill="yellow", shape=21, colour="black") +
  theme_bw() +
  coord_map(xlim=c(-56.4, -55.0), ylim=c(47.4, 47.8)) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank()) +
  scale_size_continuous(name="Total fish / sum(1/d)")

grid.arrange(plot1, plot2)

```

### DON'T DO THIS. ShortestPath uses different methods.
# Use shortestPath to make a plot
```{r}
# get spatiallines obj for shortest path
sPath1 <- shortestPath(tr3c, escapemat[1,], as.matrix(cbind(short1$x, short1$y)), output="SpatialLines")
sPath2 <- shortestPath(tr3c, testrast[2,], as.matrix(cbind(short2$x, short2$y)), output="SpatialLines")

plot(NLrast)
points(testrast, pch=16, col="red")
points(-55.5714, 47.5533, pch=16)
points(siterast)
lines(sPath1)
lines(sPath2)
points(-56.2197, 47.6495, pch=16, col="yellow") ## 22.212 km

# what about using ggplot?
# need to make a df first
# NLrastplot <- data.frame(rasterToPoints(NLrast))
# ggplot() + geom_raster(data=NLrastplot, aes(x, y, fill=as.factor(layer))) 

sPath <- shortestPath(tr3c, cbind(sitedist.join[,6], sitedist.join[,5]), cbind(sitedist.join[,2], sitedist.join[,1]), output="SpatialLines")

# ### test
# sPathtest <- shortestPath(tr3c, cbind(coastdist.join[47,2], coastdist.join[47,1]), 
#                           cbind(coastdist.join[47,6], coastdist.join[47,5]), output="SpatialLines")

??linelength
SpatialLinesLengths(sPathtest) 



plot(NLrast, xlim=c(-55.5, -55.3), ylim=c(47.6, 47.8))
lines(sPath)
points(sitedist.join[,2], sitedist.join[,1], pch=16, cex=2, col="red")
points(sitedist.join[,6], sitedist.join[,5], pch=16, col="yellow")

sitedist.join$row <- 1:length(sitedist.join$lat)
NLrastplot <- data.frame(rasterToPoints(NLrast))
ggplot() + geom_raster(data=NLrastplot, aes(x, y, fill=as.factor(layer))) + 
  geom_point(data=sites, aes(Long, Lat))+
  geom_point(data=sitedist.join, aes(long, lat, shape=as.character(row)), colour="red", size=5) +
  geom_point(data=sitedist.join, aes(siteLong, siteLat, shape=as.character(row)), colour="yellow", size=5) +
  scale_fill_manual(values=c("grey", "white")) +
  xlim(-55.5, -55.3) +
  ylim(47.6, 47.8)

```

##########################################################################################################################
#################################### NOVA SCOTIA CAGE SITE DISTANCES TEMPLATE CODE #######################################
##########################################################################################################################

## read in NS open cage site coordinates
```{r}
# sites <- read.csv("C:/Users/keyserf/Documents/Data/NL Stocking 2010-2013.csv")
# str(sites)
```

## for low-res generic mapping
```{r}
## http://ftp.geogratis.gc.ca/pub/nrcan_rncan/vector/atlas/75m_prod/geog/shape/
prov <- readShapeSpatial("./R/canvec/pvp/pvp.shp", proj4string=CRS("+proj=longlat +ellps=GRS80 +no_defs"))
#prov <- fortify(model=prov)

## Number of fish per site
ggplot() + 
  geom_polygon(data=prov, aes(long, lat, group=group), fill="grey")+
  geom_point(data=sites, aes(Long, Lat, size=Fish.Remaining...site), colour="red", shape=21) + 
  facet_wrap(~Year, nrow=4) +
  theme_bw() +
  coord_fixed(ratio=1.5, xlim=c(-57, -55), ylim=c(47, 48)) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank()) +
  scale_size_continuous(name="Number\nof fish")

## Number of cages per site
ggplot() + 
  geom_polygon(data=prov, aes(long, lat, group=group), fill="grey")+
  geom_point(data=sites, aes(Long, Lat, size=Number.of.Cages), colour="red", shape=21) + 
  facet_wrap(~Year, nrow=4) +
  theme_bw() +
  coord_fixed(ratio=1.5, xlim=c(-57, -55), ylim=c(47, 48)) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank()) +
  scale_size_continuous(name="Number\nof cages")
```

## Calculate distances between points with boundaries, need fine scale data for raster. Create raster.
## SKIP DOWN IF ENVIRONMENT IS LOADED
```{r}
## http://ftp.geogratis.gc.ca/pub/nrcan_rncan/vector/canvec/shp/Hydro/
NS.low <- readOGR(dsn = "./canvec/canvec_250K_NS_Hydro_shp/waterbody_2.shp", layer="waterbody_2")

# #cropping shapefile to the area and details I need
# NS.low.ocean <- crop(NS.low, extent(-66.7, -59.54, 43.2, 47.3))
# writeOGR(obj=NS.low.ocean, dsn="canvec", layer="NS.low.ocean", driver="ESRI Shapefile")
# rm(NS.low)

# read in cropped shapefile: NS.low.ocean
# NS.low.ocean <- readOGR(dsn="./canvec/NS.low.ocean.dbf", layer="NS.low.ocean")
# 

# break up NS into reasonable components: CB, Eastern Shore, South Shore, Northumberland. Add BOF with NB data.
NS.CB <- crop(NS.low.ocean, extent(-61.65, -59.54, 45.4, 47.1))
plot(NS.CB)

NS.ES <- crop(NS.low.ocean, extent(-63.7, -60.9, 44.5, 45.4))
plot(NS.ES)

NS.SS <- crop(NS.low.ocean, extent(-66.4, -63.35, 43.33, 44.7))
plot(NS.SS)

NS.NO <- crop(NS.low.ocean, extent(-64.88, -61.41, 45.54, 46.58))
plot(NS.NO)
# 2500 long, 1500 tall

# creating raster
#NS.CB
r <- raster(nrow=1850, ncol=1600)
extent(r) <- extent(NS.CB)
CBrast <- rasterize(NS.CB, r, fun="first")
plot(CBrast)

#NS.ES
r <- raster(nrow=1000, ncol=2200)
extent(r) <- extent(NS.ES)
ESrast <- rasterize(NS.ES, r, fun="first")
plot(ESrast)

#NS.SS
r <- raster(nrow=1650, ncol=2300)
extent(r) <- extent(NS.SS)
SSrast <- rasterize(NS.SS, r, fun="first")
plot(SSrast)

#NS.NO
r <- raster(nrow=1400, ncol=2700)
extent(r) <- extent(NS.NO)
NOrast <- rasterize(NS.NO, r, fun="first")
plot(NOrast)
```

##### START HERE IF ENVIRONMENT IS READY #####
```{r}
# site coords
# x <- 
# y <- sites$Lat
xy <- cbind(-60.869, 45.612)
siterast <- as.matrix(xy)

# test escaped fish location
# x <- -56.4
# y <- 47.5
xy <- cbind(-60.614, 45.606)
# x <- -55.7
# y <- 47.35
# xy2 <- cbind(x, y)
# xy <- rbind(xy, xy2)
testrast <- as.matrix(xy)

# SKIP IF ENVIRONMENT LOADED! change values in raster so that land is impassable (i.e. distances would be massive). 
# Also get rid of ocean blob
CBrast@data@values <- ifelse(is.na(CBrast@data@values)=="TRUE", 10000, 1)

ESrast@data@values <- ifelse(is.na(ESrast@data@values)=="TRUE", 10000, 1)
SSrast@data@values <- ifelse(is.na(SSrast@data@values)=="TRUE", 10000, 1)
NOrast@data@values <- ifelse(is.na(NOrast@data@values)=="TRUE", 10000, 1)
# rast@data@values <- ifelse(coordinates(NLrast)[,1] < -56 & coordinates(NLrast)[,2] < 47.4, 1, NLrast@data@values)
```
# Transition layer, geoCorrection, calculate distances and find shortest distance
```{r}
# create transition layer for raster (likelihood of presence within cell)
trCB <- transition(CBrast, transitionFunction=mean, directions=8)
trCBc <- geoCorrection(trCB, type="c")

# trES <- transition(ESrast, transitionFunction=mean, directions=8)
# trESc <- geoCorrection(trES, type="c", scl=TRUE)

# trSS <- transition(SSrast, transitionFunction=mean, directions=8)
# trSSc <- geoCorrection(trSS, type="c", scl=TRUE)

# trNO <- transition(NOrast, transitionFunction=mean, directions=8)
# trNOc <- geoCorrection(trNO, type="c", scl=TRUE)


# calculate least-cost distance between siterast (site location) and testrast (escaped fish location)
d <- costDistance(trCBc, fromCoords = testrast, toCoords = siterast)
d 

# pick the shortest spatiallines obj
distances <- data.frame(test1 = d[1,], test2=d[2,])
distances <- cbind(siterast, distances)
distances$shorter <- ifelse(distances$test1 < distances$test2, "test1", "test2")
short1 <- subset(distances, shorter=="test1")
short2 <- subset(distances, shorter=="test2")
```

# Use shortestPath for plotting
```{r}
# get spatiallines obj for shortest path
sPath1 <- shortestPath(trCBc, testrast, siterast, output="SpatialLines")
sPath2 <- shortestPath(trCBc, testrast[2,], as.matrix(cbind(short2$x, short2$y)), output="SpatialLines")

plot(CBrast)
points(testrast, pch=16, col="red")
points(siterast)
lines(sPath1)
lines(sPath2)

# what about using ggplot?
# need to make a df first
# NLrastplot <- data.frame(rasterToPoints(NLrast))
# ggplot() + geom_raster(data=NLrastplot, aes(x, y, fill=as.factor(layer))) 
```

########################################################################################################
################### Distances to all coastal points

### read in shoreline file and rasterize
```{r}
#getwd()
setwd("C:/Users/keyserf/Documents/")
NLline <- readOGR("C:/Users/keyserf/Documents/R/canvec/canvec_250K_NL_Land_shp/shoreline_1_small.shp", "shoreline_1_small")
extent(NLline)
NLline <- crop(NLline, extent(-57, -54, 47, 48))

r <- raster(ncol=1800, nrow=1550)
extent(r) <- extent(NLline)
NLlinerast <- rasterize(NLline, r, fun="first")
NLlinerast@data@values <- ifelse(is.na(NLlinerast@data@values)=="FALSE", 10000, NA)

plot(NLrast)
plot(NLlinerast, col="black", add=TRUE)
plot(NLlinerast, col="black")
points(-55.5714, 47.5533, col="red")
```

### convert to points dataframe
```{r}
NLpoints <- rasterToPoints(NLlinerast, spatial=TRUE)
NLpoints <- coordinates(NLpoints)

### need to fix site 47 because it is on land. move it to coast. 
ggplot() + geom_point(data=NLpoints, aes(point.long, point.lat), size=0.5) + 
  geom_point(data=sites[47,], aes(Long, Lat), colour="red") +
  coord_map() + 
  xlim(-55.5, -55.75) +
  ylim(47.4, 47.6)+
  annotate(geom="point", x=-55.605, y=47.532)

sites[47,6] <- 47.532
sites[47,7] <- -55.605

### also need to fix site 2 coords. 
ggplot() + geom_point(data=NLpoints, aes(point.long, point.lat), size=0.5) + 
  geom_point(data=sites[2,], aes(Long, Lat), colour="red") +
  coord_map() + 
  xlim(-56.5, -56.25) +
  ylim(47.6, 47.8)+
  annotate(geom="point", x=-56.325, y=47.708)

siterast[2,] <- c(-56.325, 47.708)
siterast[47,] <- c(-55.605, 47.532)
```

## calculate distances. use transition layer from polygons shapefile. find shortest distance to coast
```{r}
d <- costDistance(tr3c, fromCoords = NLpoints, toCoords = siterast)

shortest.dist <- apply(d, 2, min)
shortest.col <- apply(d, 2, which.min)

coastdist <- data.frame(lat=sites$Lat, long = sites$Long, shortest.dist = shortest.dist, shortest.col = shortest.col)

NLpoints <- data.frame(NLpoints)
NLpoints <- data.frame(shortest.col = 1:37923, point.lat = NLpoints$y, point.long = NLpoints$x)

coastdist.join <- join(coastdist, NLpoints, type="left")

write.csv(coastdist.join, "./Data/coastdist.join.csv")
```

### for plotting use shortestpath
```{r}
sPath <- shortestPath(tr3c, cbind(coastdist.join[,2], coastdist.join[,1]), cbind(coastdist.join[,6], coastdist.join[,5]), output="SpatialLines")

### test
sPathtest <- shortestPath(tr3c, cbind(coastdist.join[47,2], coastdist.join[47,1]), 
                          cbind(coastdist.join[47,6], coastdist.join[47,5]), output="SpatialLines")

??linelength
SpatialLinesLengths(sPathtest) 

plot(NLrast)
plot(NLlinerast, col="black")
lines(sPathtest)
points(coastdist.join[,2], coastdist.join[,1], pch=16, cex=2, col="red")
points(coastdist.join[,6], coastdist.join[,5], pch=16, col="yellow")
```

########################################################################################################
################### Escapes data

### read in angling locations
```{r}
bradsites <- readOGR("./Data/Angling Locations 2016.kml", "Angling Locations 2016")
plot(NLrast)
points(locs)
points(escapes$Longitude..E., escapes$Latitude..N., pch=16, col="red")


bradescapes <- read.csv("C:/Users/keyserf/Documents/Data/Escape events and reports/Gillnetting2015 - Master Copy.csv")


## mapping unknown sites from Geoff Perry

df <- read.csv("C:/Users/keyserf/Desktop/locs.csv")
df <- unique(df)
df <- arrange(df, Location)
df$num <- c(1:34)

#use prov2 shapefile from Propagule pressure.Rmd
map <- ggplot() + 
  geom_polygon(data=prov2, aes(long, lat, group=group), fill="grey")+
  annotate(geom="rect", xmin=-59.7, xmax=-56, ymin=46.6, ymax= 47.45, fill="grey") +
  annotate(geom="rect", xmin=-54, xmax=-52.6, ymin=50, ymax= 51.8, fill="grey") +
  annotate(geom="rect", xmin=-56, xmax=-55.5, ymin=46.6, ymax= 46.8, fill="grey") +
  geom_point(data=df, aes(Long, Lat)) +
  geom_label_repel(data=df, aes(Long, Lat, label=num), size=3, point.padding = unit(0.1,"lines"), min.segment.length = unit(0.1, "lines"),) +
  coord_map(xlim=c(-58, -54), ylim=c(46.8, 48.5)) +
  theme_classic() +
  theme(panel.background = element_blank(), panel.border=element_rect(colour="black", fill=NA))

labels <- ggplot() + geom_text(data=df, aes(1, Location, label=num)) + theme_classic() + ylab(NULL) + xlab(NULL) + theme(axis.text.x = element_blank(), axis.ticks = element_blank(), axis.line = element_blank())

grid.arrange(map, arrangeGrob(labels), ncol=2, widths=c(1, 0.2))

## Read in Geoff's escape reports db

geoescapes <- read.csv("C:/Users/keyserf/Documents/Data/Escape events and reports/NL Escapee database.csv")

str(geoescapes)

head(geoescapes)
geoescapes$Year <- as.numeric(as.character(geoescapes$Year))
geoescapes$Number <- as.character(geoescapes$Number)

clean <- function(i) { 
  temp=gsub(pattern=",", replacement="",x=i)
  temp=gsub(pattern=" ", replacement="",x=temp)
  temp=gsub(pattern="'", replacement="",x=temp)
  return(temp)
}

geoescapes[]<- sapply(geoescapes, clean)
geoescapes$Number.adj <- as.numeric(as.character(geoescapes$Number))
geoescapes$Size.adj <- as.numeric(as.character(geoescapes$Size))
geoescapes$Size.bin <- ifelse(geoescapes$Size.adj > 1000 | geoescapes$Size %in% c("mkts", "near-mkt"), "large", ifelse(geoescapes$Size.adj < 1001, "small", NA))
str(geoescapes)
geoescapes$ID <- as.character(geoescapes$ID)
colnames(geoescapes)[11] <- "Longitude"
colnames(geoescapes)[12] <- "Latitude"
geoescapes$Year <- as.numeric(geoescapes$Year)


geoescapes <- join(geoescapes, sitecoords, type="left")

geoescapes$Long <- ifelse(is.na(geoescapes$Long)==TRUE, geoescapes$Longitude, geoescapes$Long)
geoescapes$Lat <- ifelse(is.na(geoescapes$Lat)==TRUE, geoescapes$Latitude, geoescapes$Lat)

ggplot() + geom_point(data=geoescapes, aes(Year, Number, colour=Farm))


ggplot() + 
  geom_polygon(data=prov2, aes(long, lat, group=group), fill="grey")+
  annotate(geom="rect", xmin=-59.7, xmax=-56, ymin=46.6, ymax= 47.45, fill="grey") +
  annotate(geom="rect", xmin=-54, xmax=-52.6, ymin=50, ymax= 51.8, fill="grey") +
  annotate(geom="rect", xmin=-56, xmax=-55.5, ymin=46.6, ymax= 46.8, fill="grey") +
  geom_point(data=geoescapes, aes(Long, Lat, size=Number)) +
  coord_map(xlim=c(-58, -54), ylim=c(46.8, 48.5)) +
  theme_classic() +
  theme(panel.background = element_blank(), panel.border=element_rect(colour="black", fill=NA)) +
  facet_wrap(~Size.bin)


ggplot() + 
  geom_polygon(data=prov2, aes(long, lat, group=group), fill="grey")+
  annotate(geom="rect", xmin=-59.7, xmax=-56, ymin=46.6, ymax= 47.45, fill="grey") +
  annotate(geom="rect", xmin=-54, xmax=-52.6, ymin=50, ymax= 51.8, fill="grey") +
  annotate(geom="rect", xmin=-56, xmax=-55.5, ymin=46.6, ymax= 46.8, fill="grey") +
  geom_point(data=geoescapes, aes(Long, Lat)) +
  coord_map(xlim=c(-58, -54), ylim=c(46.8, 48.5)) +
  theme_classic() +
  theme(panel.background = element_blank(), panel.border=element_rect(colour="black", fill=NA))

geoescapes$Other.Observations <- as.character(geoescapes$Other.Observations)
geoescapes$Other.Observations[geoescapes$Other.Observations==""] <- NA
observ <- subset(geoescapes, is.na(Other.Observations)==FALSE)

options(scipen=999)

ggplot() + 
  geom_point(data=geoescapes, aes(Year, Number.adj, colour=as.factor(Location))) +
  theme_classic() +
  theme(panel.background = element_blank(), panel.border=element_rect(colour="black", fill=NA)) + 
  ylab("Number of fish") +
  scale_x_continuous(breaks=seq(1980, 2015, by=5))

str(geoescapes)
```